### 2024-05-04 paper/sec/0_abstract.tex
revised abstract

\begin{abstract}
Physical therapy can be likened to a 'rite of passage' that many people go through
because of how common it is. It provides a solution to the patient's problem, whether
that be back pain or a broken leg, but patients must be able to complete their assigned
recovery plans in order to fully heal. To optimize patient recovery, we propose a novel
approach to navigating their recovery plans utilizing computer vision techniques. By
breaking down instruction videos into vectorized representations, we can break down the
patient's videos similarly and compare the two, providing feedback and showing the
patient's progress over time, thus providing motivation in their journey.
\end{abstract}

>>>>

\begin{abstract}
For many individuals facing health hurdles, from common ailments to severe injuries, physical therapy 
represents a beneficial routine that provides a tangible path to recovery. Because adherence to prescribed 
recovery plans is critical, we present a novel application of computer vision techniques to supplement the 
traditional physical therapy experience. Whereas many recent attempts to integrate technology have involved 
passive data-logging or costly equipment, we aim to provide a cheap but interactive experience revolving 
around two key features: 1) offer quantitative feedback by scoring patients’ poses and movements against 
their exercise videos and 2) empower users to curate personalized therapy routines by filtering a database 
of physical therapy videos with specific poses. In providing a measure of progress and facilitating 
selection of progressive exercises, we hope to encourage adherence to therapy plans and foster accelerated 
healing.
% Physical therapy can be likened to a 'rite of passage' that many people go through
% because of how common it is. It provides a solution to the patient's problem, whether
% that be back pain or a broken leg, but patients must be able to complete their assigned
% recovery plans in order to fully heal. To optimize patient recovery, we propose a novel
% approach to navigating their recovery plans utilizing computer vision techniques. By
% breaking down instruction videos into vectorized representations, we can break down the
% patient's videos similarly and compare the two, providing feedback and showing the
% patient's progress over time, thus providing motivation in their journey.
\end{abstract}
